%-------------------------
% Template
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Emily Perica}

    \vspace{1pt}
    \textbf{\small 5th Year Software Engineering Co-op Student} \\ 
    \vspace{1pt}
    \small 905-580-5170 $|$ \href{mailto:emilyperica@gmail.com}{\underline{emilyperica@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/emily-perica/}{\underline{linkedin.com/in/emily-perica}} $|$
    \href{https://github.com/emilyperica}{\underline{github.com/emilyperica}}
\end{center}


%-----------EDUCATION-----------
\section{Education}

\resumeSubHeadingListStart
  \resumeSubheading{McMaster University}{Sept 2020 -- Apr 2025}{Bachelor of Engineering, Software Engineering Co-op}{Hamilton, ON}
    \resumeItemListStart
      \resumeItem{\textbf{CGPA}: 3.6}
    \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}

\resumeSubHeadingListStart
  \resumeSubheading{Wealthsimple}{May 2024 -- Aug 2024}{Application Security Developer Intern}{Toronto, ON}
    \resumeItemListStart
      \resumeItem{Developed and deployed an internal microservice with \textbf{Ruby on Rails}, \textbf{AWS ECR}, and \textbf{ArgoCD} to replace external infrastructure for hosting security automations.}
      \resumeItem{Played a key role in deploying SAST, SCA, and secrets detection tools across CI/CD pipelines, working closely with feature and DevOps teams to automate \textbf{vulnerability detection} and safeguard sensitive information.}
    \resumeItemListEnd
  \resumeSubheading{SOTI}{Jan 2023 -- Aug 2023}{Software Developer Intern}{Missisauga, ON}
    \resumeItemListStart
      \resumeItem{Developed an internal tool in \textbf{C\#} with \textbf{ASP.NET}, integrated with Jenkins and GitHub APIs, to improve backend error detection. Reduced error discovery time by \textbf{50\%} and resource costs by \textbf{75\%}.}
      \resumeItem{Conducted API testing and developed unit and integration tests in C\# for \textbf{BDD with Cucumber}, integrating them into a CI/CD Jenkins pipeline to reduce technical debt and improve test coverage.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Extracurriculars-----------
\section{Extracurriculars}

\resumeSubHeadingListStart
    \resumeSubheading{McMaster EcoCAR}{Oct 2022 -- Present}{Automatic Intersection Navigation (AIN) Lead}{}
      \resumeItemListStart
        \resumeItem{Led the development of an Automatic Intersection Navigation controller for the autonomous driving system of a customized Cadillac Lyriq, overseeing end-to-end implementation from initial design to deployment.}
        \resumeItem{Developed \textbf{C++} algorithms for intersection state detection, as well as intersection approach and departure, enhancing safety and accuracy at connected intersections.}
        \resumeItem{Built a data processing pipeline to parse \textbf{V2X} (Vehicle-to-Everything) data, isolating signal phase and spatial details for intersection path planning.}  
        \resumeItem{Defined AIN system requirements and designed \textbf{SIL} (Software-in-the-Loop) testing protocols, ensuring the safety and reliability of critical autonomous driving features.}
      \resumeItemListEnd
  \resumeSubheading{Software Engineering Society}{Mar 2022 -- Present}{VP External}{2022-2023}
    \resumeItemListStart
      \resumeItem{Organized and led multiple professional development events, including a Co-op Panel and Industry Night, to support students' career growth and industry readiness.}
      \resumeItemListEnd
  \vspace{-2pt}
  \resumeSubSubheading{VP Academic}{2023-2024}
    \resumeItemListStart
      \resumeItem{Facilitated meaningful changes in a 2nd year course by engaging in dicussions with both faculty and students, gathering feedback, and collaboratively addressing concerns to enhance the learning experience.}
    \resumeItemListEnd
  \vspace{-2pt}
  \resumeSubSubheading{VP Administration}{2024-2025}
    \resumeItemListStart
      \resumeItem{Chaired weekly meetings, coordinating with executives to strategize and implement impactiful society initiatives.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}

\resumeSubHeadingListStart
  \resumeProjectHeading{\textbf{Secure Chat Application}}{Jan 2024 -- Apr 2024}
  \resumeItemListStart
    \resumeItem{Developed an \textbf{AES-256} implementation in Java for an encrypted chat application.}
    \resumeItem{Utilized \textbf{MVC} architecture for modularity and maintainability between the frontend, backend, and data store.}
    \resumeItem{Conducted requirements elicitation to develop functional and non-functional requirements, as well as use cases to define system interactions and user needs.}
  \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}

\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: Java, Python, C\#, C/C++, Ruby, SQL, R, MATLAB, Bash, Go} \\
    \textbf{Frameworks}{: JUnit, NUnit, Pytest, Cucumber, Rails, ASP.NET} \\
    \textbf{Developer Tools}{: Git, Docker, AWS, Jenkins, GitHub Actions, Jira, Kubernetes, ArgoCD} \\
  }}
 \end{itemize}


\end{document}
